The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-24 repeater-vladata.tex
looking good on the rate!

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. 
**magnetar birth?**
Also, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

@@

The calculation of a volumetric rate has been used to identify classes of transient and their defining physical processes \citep{2006ARA&A..44..507W}. \citet{2013Sci...341...53T} used this approach to estimate an isotropic rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming a characteristic redshift horizon of 0.9 and a typical Milky Way-like galaxy host. This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.

This conclusion is in tension with new models inspired by multi-wavelength associations to \frb. Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar in a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
**biased tracer of star formation**

We now reevaluate this rate using the properties of \frb\ as a prototype FRB. First, we recast this estimate as volumetric rate of FRB sources by including beaming and repetition effects. The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction \citep[$\sim0.1$;][]{1998MNRAS.298..625T} and $V(z)$\ is the volume out to redshift $z$. Second, the projected FRB rate is now believed to be lower than initially believed \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.

% alternatively
% Third, the measured energy distributions for \frb\ allow us to estimate their detectability out to the distances implied by their DMs.
% 
% what is the energy distribution of known FRBs assuming their DM measures distance?

Third, the largest published DM \citep[$\sim1500$\ pc cm$^{-3}$ and much higher values rumored;][]{2016MNRAS.460L..30C} may imply a larger cosmic volume for FRBs. Assuming a DM dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, this places a maximum FRB redshift on the order of 2, near the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M}. While this is consistent with magnetar models proposed for \frb, the DM may include significant contributions from the host galaxy and intervening galaxy halos \citep{2014ApJ...780L..33M}. Using an assumed horizon redshift of 2, we estimate a rate of $R_p = 10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.

This revised FRB rate still ignores multiple effects. Narrow burst spectral structure implies that observations underestimate by missing bursts that fall outside the observing band. For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, past observations (typically using bandwidths of a few hundred MHz near 1.4~GHz) would underestimate the rate by a factor of a few. The horizon scale is not well defined and can change the implied rate by a factor of $\sim5$.

For comparison, the LGRB and SLSN-I rates are orders of magnitude lower, near $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$ \citep{2012Sci...337..927G}.

%galaxy number density $\Phi(M)$
%They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1011 M$;][]{2012MNRAS.421..621B}.
%
%This isotropic FRB rate assumes a projected FRB rate at a single (observationally defined) flux limit and that no bursts repeat. Using this calculation with data from more sensitive telescopes, we might infer a higher rate. However, if we assume that \frb\ is representative of the overall FRB population, then more sensitive observations would be more likely to find repeating FRBs that would effectively depress the estimate of the underlying isotropic rate per source. In this model, these two effects partially cancel, although without a physical model it is difficult to say how well.

>>>>

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. 
**magnetar birth?**
Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}. It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments.
Also, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

@@

The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. \citet{2013Sci...341...53T} used this approach to estimate a rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming an isotropic emitter in a Milky Way-type galaxy out to a characteristic redshift horizon of 0.9. This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.

However, inferences based on this and related rates are difficult, since they are strongly dependent on the sensitivity of the telescopes. Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class. We also update the volumetric rate to use the latest projected FRB rate \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.

We recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects. The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.

The characteristic distance scale for FRBs can be inferred from the detectability of \frb. The projected FRB rate is defined for a fluence limit of 1 Jy ms which is detectable out to $z=2\ for the Parkes surveys that have detected the most FRBs. This distance is consistent with that inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C}. This assumes that DM is dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$\ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, although other contributions are likely significant \citep{2014ApJ...780L..33M}. An independent argument for a characteristic distance of $z=2$\ is that it corresponds to the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M} and most leading models for FRBs are driven by star formation \citep{2016MNRAS.462..941L,2016ApJ...826..226K,2017arXiv170104815K}.

Using an assumed horizon redshift of 2, we estimate a rate of $R_p = 10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$. Narrow burst spectral structure implies that observations underestimate by missing bursts that fall outside the observing band. For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, past observations (typically using bandwidths of a few hundred MHz near 1.4~GHz) would underestimate the rate by a factor of a few. There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}. This estimate also assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation likely plays a significant role \citep{2015MNRAS.451.3278M, CORDES}.

This revised volumetric estimate makes many assumptions, but is now appropriate for comparison to rates used for other classes of transient. The LGRB and SLSN-I rates are {\color{red}xx} and $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{?,2012Sci...337..927G}. These higher-energy transients can be considered sources of FRB-generating systems if all FRBs repeat with $N_r\approx10^3$\ with burst energies near $10^{40}$\ erg. \citep{2017arXiv170102370M} calculate the maximum number of bursts that can be powered the magnetic field of a magnetar as $\approx300$, assmuming $\Omega_b=0.1$\ and $E_b=10^{40}$\ erg. This is in rough agreement, given the assumptions required in both both the observations and modeling.
